### 2009-07-09 docs/architecture/architecture.tex
more...

A \multifab\ is a collection of \fab s at the same level of
refinement.

@@

@@

>>>>

A \multifab\ is a collection of \fab s at the same level of
refinement.  The data type of a \multifab\ is:
\begin{verbatim}
  type multifab
     integer :: dim = 0
     integer :: nboxes = 0
     integer :: nc = 1
     integer :: ng = 0
     logical, pointer :: nodal(:) => Null()
     type(layout) :: la
     type(fab), pointer :: fbs(:) => Null()
  end type multifab
\end{verbatim}

@@

A \boxarray\ is an array of boxes

@@

A \mlboxarray\ is a collection of \boxarray s at different levels of
refinement.
